\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{enumitem}

\setlist{leftmargin=*,labelsep=1em}

\begin{document}
\title{Attendance Policy of Kappa Kappa Psi}
\author{Gamma Chapter at the University of Washington}
\date{April 2013}
\maketitle

\begin{enumerate}[label=\bfseries Article \Roman*]
\item
  Each Active and Associate Member is required to attend all chapter meetings; 
  \begin{enumerate}[label=\arabic*]
  \item
    if unable to attend, a written letter to the Executive Council explaining the absence is needed by midnight (12am) prior to the meeting. 
    \begin{enumerate}[label=\alph*]
    \item
      Executive Council decides the absence should not be excused, or if no letter was written in the required time frame, the absentee will incur a fine of \$0 for the first unexcused absence, \$5 for the second unexcused absence, and \$10 for any subsequent unexcused absences.
    \end{enumerate}
  \item
    If the member expects to be more than ten (10) minutes late to a meeting or expects to leave a meeting early, notification must be given to the Executive Council at least three (3) hours prior to the meeting.
     \begin{enumerate}[label=\alph*]
    \item
     Unexcused late arrivals or early departures will incur a fine after a member accrues more than three (3). The fine will be \$5 for the fourth unexcused late arrival and/or for the fourth early departure and \$10 for any subsequent late arrivals or early departures.
    \end{enumerate}
  \item
    The Executive Council must then approve the absence, late arrival, or early departure.
    The member is not considered excused until the Recording Secretary has responded with the Executive Council’s decision.
  \end{enumerate}

\item
  Each Active and Associate Member is also required to attend all Chapter ritual ceremonies.
  If a member is unable to attend a ritual ceremony, a written letter to the Executive Council explaining the absence is needed at least one week prior to the ritual ceremony.
  The Executive Council must then approve the absence.
  If the Executive Council decides the absence should not be excused, or if no letter was written in the required time frame, the absentee will incur a fine of \$25.
  No requests for late arrival or early departure will be accepted for ritual ceremonies. A late arrival or early departure will count as an absence.

\item
  In the event that Alumni members, other members of the fraternity, or members of Tau Beta Sigma wish to attend a Chapter meeting, notification to the Executive Council must be given no later than three (3) hours before the start of the meeting unless an invitation to said members has been approved by the President.

\item
  All Members requesting Conditional status are required to follow this attendance policy until the Executive Council notifies said member about the status of their request.

\item
  In the event of an extenuating circumstance, when proper notice is not possible, the Executive Council may excuse an absence, late arrival, early departure, or permit an Alumni attendance at Chapter meetings, as well as absences from ritual ceremonies, on an individual case-by-case basis.

\item
  If an Active or Associate Member does not adhere to the Chapter Attendance Policy, said member shall meet with the Executive Council to discuss their Membership status.
\end{enumerate}
\end{document}
