\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{enumitem}
\usepackage{calc}

\setlist{leftmargin=*,labelsep=1em}

\begin{document}
\title{Attendance Policy of Kappa Kappa Psi}
\author{Gamma Chapter at the University of Washington}
\date{April 2014}
\maketitle

\paragraph{Preamble}
We the Brothers of Kappa Kappa Psi, in Order to form a more perfect Brotherhood, establish Excellence, insure Loyalty, provide for the University Bands, promote the Musical Tradition, and secure the qualities of Respect and Integrity to ourselves and our Posterity, do ordain and establish this Code of Conduct for the Gamma Chapter. 

\begin{enumerate}[label=\bfseries Article \Roman*,align=left]
  \item  It shall be the duty of each person affiliated with the Gamma Chapter (Active, Associate, Conditional, Alumni, Honorary, and Prospective) to adhere to all National, District, and Local Policies.
  \item Each Active and Associate Member of the Gamma Chapter shall adhere to the Chapter’s Attendance Policy.
 
  \item No member shall attend any Chapter function under the influence of alcohol or any controlled substance.
 
  \item Each Member shall treat all other Members with respect and brotherly love.
 
  \item It is the duty of each Member to set an example of appropriate rehearsal behavior.
 
  \item Each member shall attend all chapter meetings.
  \begin{enumerate}[label=\arabic*]
    \item If unable to attend a chapter meeting, that member shall adhere to the Attendance Policy.
    \item Each member shall attend a minimum of two (2) projects and functions of the Chapter each quarter.
  \end{enumerate}

  \item  It is the duty of each member to participate in the committee(s) they commit to. Each member shall be a member of at least one standing committee.
 
  \item  Any Member not in accordance with the Code of Conduct shall be dealt with by the Executive Council on a case-by-case basis.
\end{enumerate}
\end{document}
