\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{enumitem}
\usepackage{calc}

\newlist{ol}{enumerate}{10}
\setlist[ol]{label=\arabic*.}
\newlist{abc}{enumerate}{10}
\setlist[abc]{label=\alph*)}
\newlist{legal}{enumerate}{10}
\setlist[legal,1]{label=\arabic{section}.\arabic*}
\setlist[legal]{label*=.\arabic*}
\renewcommand \thesection{\Roman{section}}

\begin{document}
\title{The Constitution of Kappa Kappa Psi}
\author{Gamma Chapter at the University of Washington}
\date{April 2014}
\maketitle

\section*{Preamble}
Be it known that Kappa Kappa Psi, National Honorary Fraternity for College band members, is an organization operating exclusively in the field of the college and university bands, and for the following several purposes:

\begin{ol}
  \item To promote the existence and welfare of the college and university bands and to cultivate at large a wholesome respect for their activities and achievements.
  \item To honor outstanding band members through privilege of membership extended as a reward for technical achievement and appreciation for the best in music.
  \item To stimulate campus leadership and promulgate an uncompromising respect through the medium of the college band for gracious conduct, good taste, and unswerving loyalty.
  \item To foster a close relationship between college bands and promote a high average of attainment by the performance of good music and selection of worthwhile projects.
  \item To provide a pleasant and helpful social experience for all engaged in college band work and to cooperate with other musical organizations in any manner consistent with the purposes of the University of Washington.
\end{ol}

\section{Organization}
\begin{legal}
  \item
    The name of this organization shall be Kappa Kappa Psi, Honorary Band Fraternity for College and University band members, Gamma Chapter at the University of Washington.
  \item
    The Chapter shall be affiliated with Kappa Kappa Psi, National Honorary Band Fraternity for College and University band members. The Chapter shall, in all cases, be subordinate to the National Fraternity.
    This Chapter Constitution shall in no way conflict with or receive priority over the National Constitution of Kappa Kappa Psi.
  \item
    The Chapter recognizes Tau Beta Sigma as an equal affiliated organization with a parallel purpose, function and role in the college and university band setting.
  \item
     The Chapter shall operate under the authority of the Chapter Sponsor.
  \item
    The Chapter shall have jurisdiction over all dues-paying Members of the Gamma Chapter of Kappa Kappa Psi.
  \item
     The Chapter will not engage in hazing as defined in the Kappa Kappa Psi National Constitution.
  \item
    The Chapter year shall be defined as the time between Formal Chapters. 
  \item
    The first week of each quarter shall begin the Sunday prior to the first day of instruction as set by the University of Washington Academic Calendar.
  \item
    The following documents shall function in support of this Constitution:
    \begin{abc}
      \item Attendance Policy
      \item Code of Conduct
      \item Convention Fund
      \item Membership Education Program (MEP)
      \item Guide to Leadership
    \end{abc}
\end{legal}

\section{Membership}
\begin{legal}
  \item
    Chapter Membership types shall be as outlined in the National Constitution.
    No Membership shall be recognized by the Chapter until all initiation fees have been paid to the Chapter or other arrangements have been made and the initiation has been completed as prescribed by the Ritual.
  \item
    The Chapter shall not discriminate for Membership or status on the basis of race, national origin, gender, sexual orientation, religion, handicap, or marital status.
  \item
    The majority of the Active Membership of the Chapter shall consist of regularly enrolled undergraduate and graduate students of the University of Washington.
  \item
    It shall be the duty of each Active and Associate Member to adhere to the Chapter Attendance Policy and Code of Conduct; to promptly fulfill all financial obligations to both the Chapter and the National Fraternity; to become acquainted with the National Constitution, District Constitution, Joint District Constitution, Chapter Constitution and the history of Kappa Kappa Psi; to support the efforts and purposes of the Chapter and Fraternity.
\end{legal}

\section{Officers and Appointed Positions}
\begin{legal}
  \item
    The Officers of the Chapter shall be President, Vice-President, Treasurer, Recording Secretary, Corresponding Secretary, Historian, Director of Post-Membership Education and Parliamentarian.
  \item
    The Appointed Positions of the Chapter shall be Webmaster and Director of Music.
  \item
    The Chapter Officers shall together form the Executive Council of the Chapter.
    The Executive Council shall meet separately from the Active Membership as needed and shall report to the Active Membership on all relevant matters discussed at Executive Council meetings.
    A majority of all voting Chapter Officers shall constitute a quorum for all Executive Council meetings.
  \item
    The Active and Associate Members of the Chapter shall elect the officers at a regularly called meeting of the Chapter during spring quarter at such a time that all eligible members shall have a fair chance at candidacy.
    The Chapter President shall notify the entire voting Membership of the election in a meeting at least seven days prior to the election.
    Election of Chapter Officers shall require a majority of all votes cast.
    In the event that no one candidate receives a majority vote, a runoff election shall be held between the leading candidates as determined by the President and Parliamentarian.
  \item
    The responsibilities laid out for officers in this constitution are in addition to responsibilities specified in the National Constitution.
  \item
    The President shall preside at all meetings of the Chapter and shall be a Member ex officio of all Chapter Committees.
    The President shall be listed on all Chapter accounts and shall sign all contracts and other instruments of business involving the Chapter.
    The President shall be designated as the official representative of the Chapter whenever such representation shall be required and shall prepare and send all reports to the National Headquarters.
    The President shall present the agenda for the meeting and Executive Council meeting to the chapter via email at least 12 hours prior to the meeting.
  \item
    The Vice-President shall, in the absence of the President, preside at the meetings of the Chapter and shall advance the purposes of the Fraternity as stated in the Preamble of the National Constitution by promoting the work of the Chapter as performed by its several Officers and Committees.
    The Vice President shall serve as a member of the Brotherhood Committee.
    The Vice-President shall be responsible for Prospective Membership Education.
    The Vice-President shall follow the Membership Education Plan (MEP) as approved by the chapter.
    \begin{legal}
      \item
        The Vice-President will review the MEP at the beginning of each academic year.
      \item
        Any changes made to the MEP will be presented to the Chapter before First Degree and will be approved by the Chapter and Sponsor.
    \end{legal}
  \item
    The Treasurer shall control all receipts and disbursement of all monies of the Chapter, and shall submit recommendations concerning the financial policies of the Chapter as may be required.
    The Treasurer shall draft a quarterly Chapter financial budget by the second official meeting of each quarter. The Treasurer shall send out the budget to the active body within seven (7) days of approval.
    The treasurer shall serve as a member of the fundraising committee and will be eligible to apply for the fundraising committee head position. 
  \item
    The Recording Secretary shall record the minutes of all Chapter Meetings.
    The Recording Secretary shall be responsible for making sure each Member has access to a copy of meeting minutes before the next meeting.
    The Recording Secretary will be responsible for taking notes of the Executive Council meetings and making them available to Executive Council Members.
    The Recording Secretary shall maintain a permanent record of each Member of the Chapter including a name, address, class, and instrument played.
    The Recording Secretary shall serve as a member of the Publications Committee and will be eligible to apply for the Publications Committee head position.
    The Recording Secretary will be responsible for the publication of The Sundodger or the Music Note based on their preference.
  \item
    The Corresponding Secretary shall be responsible for all Chapter communication.
    The Corresponding Secretary shall be responsible for the e-mail account and will be responsible for the Chapter e-mail distribution lists.
    The Corresponding Secretary shall be responsible for Honorary and Alumni Member records and dissemination of information to those Members.
    The Corresponding Secretary shall serve as a member of the Publications Committee and will be eligible to apply for the Publications Committee head position
  \item
    The Historian shall maintain a written and pictorial record of the current activities of the Band and Chapter and actively research past Band and Chapter history.
    The Historian will be responsible for the coordination of the chapter display and scrapbook for District and National Conventions.
  \item
    The Director of Post-Membership Education (DPME) shall be responsible for the continuing education of the Chapter’s Active and Associate members.
    The DPME shall have all lessons submitted to the Executive Council for approval at least 24 hours in advance of the event at which they will occur.
    No DPME lesson shall be given without prior approval from the Executive Council.
  \item
    The Parliamentarian shall advise the Chapter and Executive Council upon all rules and policies as set forth in the Chapter and National Constitutions.
    The Parliamentarian shall have a working knowledge of the Chapter, District, Joint District, and National Constitutions.
    The Parliamentarian shall maintain the official copy of the Chapter Constitution, and have current copies of all above mentioned Constitutions available to all Active and Associate Members for reference at all Chapter meetings.
    The Parliamentarian shall be familiar with parliamentary procedure.
    The Parliamentarian shall be present for advisement at Executive Council meetings, without privilege of vote.
    The Parliamentarian shall assume the duties of leading chapter should the President need be absent for any reason. 
  \item
    The Webmaster shall be appointed, through application, by the Executive Council following each year’s election.
    The Webmaster is open to any Active or Associate Member.
    The Webmaster shall be responsible for updating the website within one week of major events or requests.
    If the request cannot be completed within one week, the Webmaster is responsible for notifying the requester for the expected time of completion.
    The Webmaster shall provide access to all Chapter publications and documents.
  \item
    The Director of Music shall be appointed, through application, by the Executive Council following each year’s election.
    The Director of Music is open to any Active or Associate Member. The Director of Music shall be responsible for the promotion of music and musicianship in the Chapter.
  \item
    The Director of Ceremonies shall be appointed, through application, by the Executive Council following each year's election.
    The Director of Ceremonies is open to any Active or Associate Member.
    The Director of Ceremonies shall: coordinate all matters pertaining to fraternal rituals and ceremonies for the chapter; be responsible for protecting the property of the Chapter; and serve as a member of the Brotherhood Committee. 
  \item
    Upon due cause a Chapter Officer or Appointed Position Holder may be removed from office following a favorable vote of three-fourths of the Chapter’s total Active Membership.
    The individual will be given a hearing in front of the Active Membership before the said motion is voted on.
    The vote will be by secret ballot.
  \item
    In the case of the vacancy of an office between regularly scheduled elections, the following procedure shall be used to fill the vacancy until the next regularly scheduled election.
    \begin{legal}
      \item
        The office of the President shall be filled by the Vice-President, leaving the office of Vice-President vacant.
      \item
        A special election will be held following the same provisions as prescribed for normal elections for the offices of Vice-President, Treasurer, Recording Secretary, Corresponding Secretary, Historian, DPME, and Parliamentarian. The positions of Webmaster and Director of Music will be filled by an Executive Council appointment.
      \item
        A vacancy in any office or appointed position will be filled immediately during a regularly scheduled Chapter meeting.
    \end{legal}
  \item
    All Chapter Officers and Appointed Position holders shall compile a report on the week’s developments for the President.
    This report will be submitted at a time designated by the President.
\end{legal}

\section{Finances}
\begin{legal}
  \item
    The financial policies of the Chapter shall be governed by a budget adopted at the beginning of each academic quarter.
    The budget must be approved by a two-thirds majority of the Chapter’s total Active Membership.
    Any major deviations from the approved budget must be approved by a two-thirds majority of the Chapter’s total Active Membership.
  \item
    Income of the Chapter shall be derived from annual dues assessed from each Active and Associate Member and fundraising projects conducted by the Chapter.
    These dues shall cover an annual National Membership fee as determined by the National Chapter and may include Chapter dues as outlined below.
    All National dues shall be paid on or before October 15th of each year.
    Members failing to pay National dues by October 15th shall be listed as Inactive on the Chapter Personnel Report.
    \begin{legal}
      \item
        Local Dues may be required on a quarter-by-quarter basis as deemed necessary by the Executive Council.
      \item
        Any Local Dues will be set by the Executive Council and must be approved by a two thirds (2/3) majority vote of the Chapter’s total Active Membership.
        Any Local dues must be set two (2) weeks prior to the start of the quarter in which they will be collected.
      \item
        Any Local Dues shall be paid by the second week of the quarter.
        Members failing to pay local dues shall meet with the Executive Council to discuss Membership Status.
    \end{legal}
  \item
    The Chapter shall pay an annual National Fraternity fee as determined by the National Fraternity and payable to the National Executive Director on or before October 15th of each year.
  \item
    The Chapter shall have and maintain a Convention Fund as outlined in the Convention Fund document.
  \item
    Any Active or Associate Member unable to meet any financial obligation to the Chapter by the obligation’s deadline shall arrange a meeting with the Executive Council prior to the deadline to make payment arrangements.
\end{legal}

\section{Committees}
\begin{legal}
  \item
    The following standing committees shall function to serve the needs of the Chapter: Service, Fundraising, Social, Brotherhood, and Publications.
    \begin{legal}
      \item 
        The Service Committee shall exist to plan and organize worthwhile projects to serve the bands of the University of Washington.
        The Service Committee shall also be responsible for eliciting the support of the Chapter to complete the projects.
      \item 
        The Fundraising Committee shall exist to plan and organize worthwhile projects to raise funds for the functions of the Chapter.
        The Fundraising Committee shall also be responsible for eliciting the support of the Chapter to complete the projects.
      \item 
        The Social Committee shall exist to carry out those projects which will increase the interactions among fellow musicians.
        Anyone involved with a band program will be welcome to participate in social events unless a specific event is predetermined to be for a select audience.
      \item 
        The Brotherhood Committee shall exist to plan and organize worthwhile events that strengthen fraternal bonds in the chapter while encouraging chapter-wide participation.
        The Brotherhood Committee shall be called upon to assist the Director of Ceremonies with the execution of fraternal rituals and ceremonies when necessary. 
      \item
        The Publications Committee shall exist to produce publications for the good of the chapter and who it serves.
        The Publications Committee shall be responsible for the Publication of the Sundodger or the Music Note (based on what the Recording Secretary chooses), Gamma Gossip, and Funpacks when necessary.
        The committee shall produce other necessary publications as determined by the committee head and committee members.
        The Publications Committee shall coordinate the submission of articles to The Accent and The Podium publications.
        The committee shall be responsible for all social media promotion and usage.
        The committee will work with the Recording Secretary and Corresponding Secretary as needed.
      \item 
        All other committees of the Chapter shall be determined as required by the Chapter.
        \begin{legal}
          \item 
            The creation of a new non-standing committee shall require a favorable majority vote of the Chapter’s total Active Membership.
          \item 
            The new Committee Head will be assigned following the provisions outlined in section \ref{committeehead}.
        \end{legal}
    \end{legal}
  \item
    \label{committeehead}
    All Committee Heads shall be nominated by the Executive Council and shall be presented to the Chapter for approval.
  \item
    New Committee Heads will be selected for all committees, except temporary committees, each spring quarter after the election of the new Executive Council following the same provisions outlined in \ref{committeehead}.
  \item
    All Committees are responsible to meet as deemed necessary by a simple majority of the committee and announce the time and location of meetings at a regularly scheduled meeting of the Chapter.
  \item
    All Committee Heads shall compile a report on the week’s developments for the President.
    This report will be submitted at a time designated by the President.
    All Committees are responsible to report on Committee business at each regularly scheduled Chapter Meeting.
  \item
    Upon due cause a Committee Head may be removed from their position following a favorable vote of three-fourths of the Chapter’s total Active Membership.
    The individual will be given a hearing in front of the Active Membership before the said motion is voted on.
    The vote will be by secret ballot.
  \item
    In the case of the vacancy of a Committee Head position between regularly scheduled elections, a new Committee Head will be put in place following the same provisions outlined in section \ref{committeehead}.
  \item
    Upon due cause a non-standing Committee may be disbanded following a favorable vote of a majority of the Chapter’s total Active Membership.
    A discussion on the necessity and purpose of said committee will take place before the motion is voted on.
    The vote will be by secret ballot unless a majority of the Active Membership present agrees otherwise.
\end{legal}

\section{Meetings}
\begin{legal}
  \item
    A regularly called meeting of the Chapter shall be held at least twice a month during the regular school year.
    Meetings may be held more frequently when deemed advisable by the Chapter.
    The exact time and location of the meeting shall be announced by the Chapter President prior to the meeting.
  \item
    Special Chapter meetings shall be called as needed by the Executive Council.
  \item
    A Formal Chapter shall be held during Spring Quarter following the regularly called meeting of the Chapter in which the officers are elected.
    The purpose of this Formal Chapter being to install the elected Executive Council. 
    \begin{legal}
      \item
        A Formal Chapter will not be held to install an officer elected to fill a vacancy.
    \end{legal}
  \item
    The Recording Secretary shall take roll at each meeting.
  \item
    One-half of all Active and Associate Members in the Chapter together with at least three Chapter Officers shall constitute a quorum at all meetings.
  \item
    Unless otherwise specified in this Constitution, all business shall be decided by a simple majority of all votes cast, omitting abstentions. If one-third of total votes cast are abstentions, discussion must continue.
  \item
    Any Active who has an excused absence from a Chapter meeting may assign another Active to serve as their proxy
    \begin{legal}
      \item
        The proxy assignment shall be approved by the President on a case-by-case basis.
    \end{legal}
  \item
    In general, the order of business of all Chapter meetings shall be:
    \begin{abc}
      \item 
        Opening Ceremonies
      \item 
        Approval of Minutes
      \item 
        Report of Committees
      \item 
        Report on Chapter Officers
      \item 
        Goal Development and Review
      \item 
        Old Business
      \item 
        New Business
      \item 
        Closing Ceremonies
    \end{abc}
    When deemed advisable, the general order of business may be changed at the discretion of the Chapter President.
\end{legal}

\section{Amendments}
\begin{legal}
  \item
    Any part of this Constitution or its supporting documents may be amended at any time by a two thirds (2/3) vote of all eligible voting members of the Chapter.
    \begin{legal}
      \item
        If the favorable vote on a proposed amendment is less than two thirds (2/3) majority, yet there is an absolute majority vote, the proposed amendment shall be tabled until the next regularly scheduled review of this Constitution.
      \item
        If two thirds (2/3) of the votes cast by the members are favorable, the proposed amendment shall be declared adopted, and shall become operative and effective at the conclusion of the meeting unless otherwise noted.
      \item
        Proposed amendments shall be presented in writing to the Chapter at least seven (7) days prior to their consideration.
      \item
        The Chapter Parliamentarian shall assemble a Jurisdiction Committee to review all Chapter Documents at least once a year. This review will occur before Chapter Officer elections.
    \end{legal}
\end{legal}
\end{document}
